---
output: github_document
---
```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>')
```

# examinr R package

<!-- begin badges -->

<!-- [![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/examinr)](https://CRAN.R-project.org/package=examinr) -->
![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)
![CRAN Status: not yet released](https://img.shields.io/badge/CRAN-not%20yet%20released-red.svg)
```{r, results='asis', echo=FALSE, eval=TRUE}
branch_name <- Sys.getenv('GIT_BRANCH', '')
if (nchar(branch_name) == 0L) {
  branch_name <- tryCatch(system('git rev-parse --abbrev-ref HEAD', intern = TRUE),
                          error = function (e) { warning("error: ", as.character(e));  return('master') },
                          warning = function (w) { warning("warning: ", as.character(w)); return('master') })
}
cat(sprintf('[![Build Status](https://travis-ci.com/dakep/examinr.svg?branch=%s)](https://travis-ci.com/dakep/examinr)',
            branch_name))
```
<!-- end badges -->

Create gradable exams as interactive Shiny documents from R markdown documents.
Learners can attempt an exam one or more times, and each attempt uses a (potentially) different random seed to generate the question text and answers.

For a full list of features and to learn how to create your own exams, visit the documentation at [https://dakep.github.io/examinr](https://dakep.github.io/examinr/articles/examinr.html).

## Installation

The package is still in development and not yet available on CRAN.
You can install it via

```r
devtools::install_github("dakep/examinr")
```

## Highlights

- Questions and text are rendered on-demand for each attempt:
  * Allows for user- and attempt-specific content (e.g., randomized values in questions and answers)
  * Questions are not sent to the user's browser until they are allowed to see them
- Support for different question types:
  * Simple text answers
  * R code exercises
  * Numeric answers (with auto-grading support)
  * Multiple-choice (with auto-grading support)
- Users are authenticated via configurable authentication providers
- Exams can be configured to show only one section at a time
- Fine-grained control over attempts:
  * Control how many attempts each user gets
  * Configure exams to be only accessible after the opening time and until the closing time
  * Timed attempts where users are required to submit the exam within the specific time limits
  * Adjust the configuration for specific users
- Support for message localization
- Interfaces for grading (for instructors) and for accessing feedback (for users).
- High-contrast theme and screen-reader friendly output
- Users' inputs are also stored in their browser to allow restoring input values after a reload or in case of server issues.

## Features to be added

The package is still in a development phase and some features are not yet available, most notably the following:

- File upload question.
- Multiple text inputs per text question.
- Improved rendering of help pages.
- Support auto-grading of code exercises.

If you are looking for specific features which are not yet supported by examinr and not yet requested, please create an [issue](https://github.com/dakep/examinr/issues) or, even better, a [pull request](https://github.com/dakep/examinr/pulls).

## Acknowledgments

Several features in examinr are inspired by the [learnr](https://github.com/rstudio/learnr) package, in particular the exercises.
