---
output: github_document
---
```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>')
```

# examinr R package

<!-- begin badges -->
<!-- [![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/examinr)](https://CRAN.R-project.org/package=examinr) -->
```{r, results='asis', echo=FALSE, eval=TRUE}
branch_name <- Sys.getenv('GIT_BRANCH', '')
if (nchar(branch_name) == 0L) {
  branch_name <- tryCatch(system('git rev-parse --abbrev-ref HEAD', intern = TRUE),
                          error = function (e) { warning("error: ", as.character(e));  return('master') },
                          warning = function (w) { warning("warning: ", as.character(w)); return('master') })
}
cat(sprintf('[![Build Status](https://travis-ci.com/dakep/examinr.svg?branch=%s)](https://travis-ci.com/dakep/examinr)',
            branch_name))
```
<!-- end badges -->

Easily create exams in R by writing Rmarkdown files as interactive shiny documents.

## TODO

- "visual" authentication provider, i.e., one with a login UI
- grading
  * _live_ grading of answers at the end of the exam
  * _automatic_ grading of auto-gradable questions
  * interface for manual grading

## Notes

- Every R code chunk which should **not** be evaluated in the user's session, must have option `exam.static = TRUE` set.
  This option cannot be set globally for all code chunks.
- Exercise code chunks are defined via chunk option `exercise=TRUE` and support all options listed in [exercise_options()].
- Clicking on the *last visible* "next section button" will mark an attempt as finished.
